\chapter*{Acknowledgement}
The group would like to express its sincere gratitude to the instructor of the Object-Oriented Programming course, who has devotedly imparted fundamental knowledge and guided the group throughout the implementation of this term project.

The lectures on object-oriented principles, together with valuable professional feedback, helped the group not only complete the product but also develop a systematic and scientific approach to software design. This is an important foundation that gives each member greater confidence on the path of study and future professional development.

During the implementation, due to limitations in time and knowledge, this report may contain shortcomings. The group sincerely looks forward to receiving comments from the instructor in order to improve the topic further.

The group sincerely thanks you!

\chapter*{Abstract}
This report presents the process of analysing, designing, and implementing a \textbf{Financial Transaction Management \& Audit System} in the C++ programming language, strictly following the principles of Object-Oriented Programming (OOP).

The system simulates a real-world banking problem: automatically scanning large volumes of transactions to detect signs of financial fraud such as money laundering and the splitting of cash flows (\textit{smurfing}). Architecturally, the system is divided into four independent functional modules and fully applies object-oriented techniques: abstraction through abstract classes and interfaces, single and multiple inheritance, polymorphism via dynamic dispatch, together with advanced memory-management techniques such as the Rule of Five and the Virtual Constructor idiom.

Experimental results show that the system operates stably, accurately detects violating transactions under several types of audit rules, is free of memory leaks, and clearly demonstrates extensibility -- a new audit rule can be added without modifying the core source code of the system.

\textbf{Keywords:} Object-Oriented Programming, C++, Polymorphism, Multiple Inheritance, Memory Management, Financial Fraud Detection.
